Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2017-06-05 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
modified some figures, maybe now closer to what reviewer wanted?

The multi-fidelity domain refinements for the five adaptive iterations are shown in \Cref{fig:divvy3D_diffmesh}. Similarly to the behavior seen in \Cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to receive refinement. We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_1$ ($5.2\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff.png}
}
\subfloat[MF$_2$ ($11.4\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff.png}
}
\subfloat[MF$_3$ ($16.3\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy3_whitebg_puff.png}
} \\
\subfloat[MF$_4$ ($22.0\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy4_whitebg_puff.png}
}
\subfloat[MF$_5$ ($27.7\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff.png}
}
\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
\label{fig:divvy3D_diffmesh}
\end{figure}
%

>>>>

The multi-fidelity domain refinements for the five adaptive iterations are shown in \Cref{fig:divvy3D_diffmesh}. Similarly to the behavior seen in \Cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to receive refinement. We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
%
\begin{figure}[htbp]
\centering
\subfloat[Slice location]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/slice_diagram.png}
}
\hfill
\subfloat[MF$_1$ ($5.2\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff_and_midslice.png}
}
\\
\subfloat[MF$_2$ ($11.4\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff_and_midslice.png}
} 
\hfill
\subfloat[MF$_3$ ($16.3\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy3_whitebg_puff_and_midslice.png}
} \\
\subfloat[MF$_4$ ($22.0\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy4_whitebg_puff_and_midslice.png}
} 
\hfill
\subfloat[MF$_5$ ($27.7\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff_and_midslice.png}
}

\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
\label{fig:divvy3D_diffmesh}
\end{figure}
%
